---
title: "PfS / DDPI Staff Assessment"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r read, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(dplyr)
library(reshape2)

survey = read.csv('data.csv', stringsAsFactors = FALSE)
survey <- survey[3:30,]
survey<- data.frame(data.matrix(survey))
```

##Aggregate report for all participants

```{r create results, echo=FALSE, warning=FALSE, message=FALSE}
Current <- data.frame(survey[,'Q4.2_1'],
survey[,'Q4.3_1'],
survey[,'Q4.4_1'],
survey[,'Q4.5_1'],
survey[,'Q4.6_1'],
survey[,'Q4.7_1'],
survey[,'Q4.8_1'],
survey[,'Q4.9_1'],
survey[,'Q4.10_1'],
survey[,'Q4.11_1'],
survey[,'Q4.12_1'],
survey[,'Q4.13_1'],
survey[,'Q4.14_1'],
survey[,'Q4.15_1'],
survey[,'Q4.16_1'],
survey[,'Q6.2_1'],
survey[,'Q6.3_1'],
survey[,'Q6.4_1'],
survey[,'Q6.5_1'],
survey[,'Q6.6_1'],
survey[,'Q7.2_1'],
survey[,'Q7.3_1'],
survey[,'Q7.4_1'],
survey[,'Q7.5_1'],
survey[,'Q7.6_1'],
survey[,'Q7.7_1'],
survey[,'Q7.8_1'],
survey[,'Q8.2_1'],
survey[,'Q8.3_1'],
survey[,'Q8.4_1'],
survey[,'Q9.2_1'],
survey[,'Q9.3_1'],
survey[,'Q10.2_1'],
survey[,'Q10.3_1'],
survey[,'Q10.4_1'],
survey[,'Q10.5_1'],
survey[,'Q10.6_1'],
survey[,'Q11.2_1'],
survey[,'Q11.3_1'],
survey[,'Q12.2_1'],
survey[,'Q12.3_1'],
survey[,'Q12.4_1'],
survey[,'Q12.5_1'],
survey[,'Q12.6_1'],
survey[,'Q12.7_1'],
survey[,'Q13.2_1'],
survey[,'Q13.3_1'],
survey[,'Q13.4_1'],
survey[,'Q13.5_1'],
survey[,'Q13.6_1'],
survey[,'Q13.7_1'],
survey[,'Q13.8_1'],
survey[,'Q13.9_1'])

Desired <- data.frame(survey[,'Q4.2_2'],
survey[,'Q4.3_2'],
survey[,'Q4.4_2'],
survey[,'Q4.5_2'],
survey[,'Q4.6_2'],
survey[,'Q4.7_2'],
survey[,'Q4.8_2'],
survey[,'Q4.9_2'],
survey[,'Q4.10_2'],
survey[,'Q4.11_2'],
survey[,'Q4.12_2'],
survey[,'Q4.13_2'],
survey[,'Q4.14_2'],
survey[,'Q4.15_2'],
survey[,'Q4.16_2'],
survey[,'Q6.2_2'],
survey[,'Q6.3_2'],
survey[,'Q6.4_2'],
survey[,'Q6.5_2'],
survey[,'Q6.6_2'],
survey[,'Q7.2_2'],
survey[,'Q7.3_2'],
survey[,'Q7.4_2'],
survey[,'Q7.5_2'],
survey[,'Q7.6_2'],
survey[,'Q7.7_2'],
survey[,'Q7.8_2'],
survey[,'Q8.2_2'],
survey[,'Q8.3_2'],
survey[,'Q8.4_2'],
survey[,'Q9.2_2'],
survey[,'Q9.3_2'],
survey[,'Q10.2_2'],
survey[,'Q10.3_2'],
survey[,'Q10.4_2'],
survey[,'Q10.5_2'],
survey[,'Q10.6_2'],
survey[,'Q11.2_2'],
survey[,'Q11.3_2'],
survey[,'Q12.2_2'],
survey[,'Q12.3_2'],
survey[,'Q12.4_2'],
survey[,'Q12.5_2'],
survey[,'Q12.6_2'],
survey[,'Q12.7_2'],
survey[,'Q13.2_2'],
survey[,'Q13.3_2'],
survey[,'Q13.4_2'],
survey[,'Q13.5_2'],
survey[,'Q13.6_2'],
survey[,'Q13.7_2'],
survey[,'Q13.8_2'],
survey[,'Q13.9_2'])

Competency = c('PDMP Statutes and Laws',
'PDMP Implementation/Expansion',
'PDMP Data Sharing and Linking',
'PDMP Integration with Pharmacy Software',
'PDMP Interstate Data Sharing',
'Heroin/Fentanyl',
'Insurance Mechanisms',
'CDC Prescribing Guideline',
'Academic Detailing',
'Naloxone',
'PfS Indicators',
'ICD-10-CM Transition',
'Data Dashboards',
'Program Evaluation',
'Legal/Policy Tools',
'Monthly 1:1 Calls with Awardees',
'APRs/TRs',
'Site Visits ',
'Financial Award Management',
'Understanding of Role',
'Monthly 1:1 Calls with Awardees',
'Responsiveness to Scientific TA Requests',
'Using Quantitative Analytic Techniques',
'Using Qualitative Analytic Techniques',
'Annual Progress Reports / Technical Reviews',
'Site Visits',
'Understanding  of Role',
'Monthly 1:1 Calls with Awardees',
'APRs/TRs',
'Site Visits',
'Support to States',
'Support to SSTs',
'Relationship Building w/ States',
'Relationship Building w/Program Partners',
'Relationship Building w/in State Support Teams',
'Effective Communication',
'Conflict Management/Resolution',
'Accountability',
'Ongoing Learning and Professional Development',
'Program Development, Improvement and Evaluation',
'Fostering Collaboration and Leveraging Resources',
'Time Management',
'Providing TA to States',
'Decision Making',
'Individual Project Management',
'Program Evaluation',
'Engaging Stakeholders',
'Describing the Program/Project',
'Focusing the Evaluation Design',
'Development of IRB and OMB Packages',
'Gathering Credible Evidence',
'Justifying Conclusions',
'Ensuring Use and Sharing Lessons Learned')

Section = c('Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Project Officer',
'Project Officer',
'Project Officer',
'Project Officer',
'Project Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Evaluation Officer',
'Evaluation Officer',
'Evaluation Officer',
'Subject Matter Expert',
'Subject Matter Expert',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Professionalism',
'Professionalism',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation')

Part = c('A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B')

results <- data.frame(Competency,Part,Section)

colnames(Current) <- Competency
colnames(Desired) <- Competency

Current[Current == 7] <- NA
Desired[Desired == 7] <- NA

results$Current <- colMeans(Current, na.rm = TRUE)
results$Desired <- colMeans(Desired, na.rm = TRUE)
results$Difference <- results$Desired - results$Current

```
The PfS / DDPI Staff Assessment survey was divided into three parts, including:

- **Part A: Topical and Role-Specific Competencies**
- **Part B: Functioning Competencies**
- **Part C: Skills, Knowledge, and Processes Important to You**

###Part A: Topical and Role-Specific Competencies

####Section 1: Topical Competencies

For **Part A** of the PfS / DDPI Staff Assessment survey all participants were asked to rate their **Current** and **Desired** level for each of a set of listed competencies.

- **Current** skill level was defined as your present level of competency in a particular skill or area
- **Desired** level was defined as the level of ability you were interested in attaining for a particular skill or knowledge area in the future

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Topical Competencies**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Overall Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%"}
library(ggplot2)
filter(results, Section == "Topical") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., desc(variable), desc(value)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Topical Competencies") +
  theme(legend.position='top')
```

\newpage

#####Key Strengths

The table below shows the **Topical Competencies** with the highest reported **Current** skill levels. These competencies reflect areas of relative strength.

```{r Strengths Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Topical" & Current > 3.5) %>%
  select(Competency, Current) %>%
  arrange(., desc(Current)) %>%
  kable(.,digits = 2)
```

#####Key Deficits

The table below shows the **Topical Competencies** with the lowest reported **Current** skill levels. These competencies reflect important areas where more training may be neccesary.

```{r Deficits Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Topical" & Current < 2.5) %>%
  select(Competency, Current) %>%
  arrange(., Current) %>%
  kable(.,digits = 2)
```

#####Areas of Desired Growth

The table below shows **Topical Competencies** with the highest degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Desired Growth Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Topical" & Difference > 1.49) %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

####Section 2: Role-Specific Competencies

#####Project Officers

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Role-Specific Competencies** for **Project Officers**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Project Officer Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=3}
filter(results, Section == "Project Officer") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., Competency, desc(variable)) -> graph

ggplot(graph, aes(x = reorder(Competency, value), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Project Officer Role-Specific Competencies") +
  theme(legend.position='top')
```

The table below shows all **Role-Specific Competencies** for **Project Officers** sorted by the degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Project Officer Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Project Officer") %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

#####Science Officers

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Role-Specific Competencies** for **Science Officers**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Science Officer Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=4}
filter(results, Section == "Science Officer") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., Competency, desc(variable)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Science Officer Role-Specific Competencies") +
  theme(legend.position='top')
```

The table below shows all **Role-Specific Competencies** for **Science Officers** sorted by the degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Science Officer Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Science Officer") %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

#####Evaluation Officers

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Role-Specific Competencies** for **Evaluation Officers**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Evaluation Officer Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=2.5}
library(ggplot2)
filter(results, Section == "Evaluation Officer") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., Competency, desc(variable)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Evaluation Officer Role-Specific Competencies") +
  theme(legend.position='top')
```

The table below shows all **Role-Specific Competencies** for **Evaluation Officers** sorted by the degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Evaluation Officer Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Evaluation Officer") %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

#####Subject Matter Experts

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Role-Specific Competencies** for **Subject Matter Experts**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Subject Matter Expert Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=2}
library(ggplot2)
filter(results, Section == "Subject Matter Expert") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., Competency, desc(variable)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Subject Matter Expert Role-Specific Competencies") +
  theme(legend.position='top')
```

The table below shows all **Role-Specific Competencies** for **Subject Matter Experts** sorted by the degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Subject Matter Expert Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Section == "Subject Matter Expert") %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

###Part B: Functioning Competencies

For **Part B** of the PfS / DDPI Staff Assessment survey all participants were asked to again rate their **Current** and **Desired** level for each of a set of listed **Functioning Competencies**.

The **Functioning Competencies** were categorized into four key areas:

 - Interpersonal Skills
 - Professionalism
 - Program Management
 - Evaluation

The table below shows all **Functioning Competencies** sorted within their respective categories by the degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r Functional Competencies Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Part == "B") %>%
  select(Competency, Section, Current, Desired, Difference) %>%
  arrange(., desc(Section), desc(Difference)) %>%
  kable(.,digits = 2)
```

Competencies with a high degree of difference between **Current** and **Desired** levels represent areas of desired growth among employees, on average, and therefore may constitute important areas for future trainings.

\newpage

#####Key Strengths

The table below shows the **Functional Competencies** with the highest reported **Current** skill levels. These competencies reflect areas of relative strength.

```{r B Strengths Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Part == "B" & Current > 4.5) %>%
  select(Competency, Current) %>%
  arrange(., desc(Current)) %>%
  kable(.,digits = 2)
```

#####Key Deficits

The table below shows the **Functional Competencies** with the lowest reported **Current** skill levels. These competencies reflect important areas where more training may be neccesary.

```{r B Deficits Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Part == "B" & Current < 3.75) %>%
  select(Competency, Current) %>%
  arrange(., Current) %>%
  kable(.,digits = 2)
```

#####Areas of Desired Growth

The table below shows **Functional Competencies** with the highest degree of *Difference* between average reported **Current** and **Desired** skill levels.

```{r B Desired Growth Table,  echo=FALSE, warning=FALSE, message=FALSE}
filter(results, Part == "B" & Difference > 1.25) %>%
  select(Competency, Current, Desired, Difference) %>%
  arrange(., desc(Difference)) %>%
  kable(.,digits = 2)
```

\newpage

####Interpersonal Skills

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Interpersonal Skills**. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Interpersonal Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=2.8}
library(ggplot2)
filter(results, Section == "Interpersonal") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., desc(variable), desc(value)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Interpersonal Skills") +
  theme(legend.position='top')
```

####Professionalism

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Professionalism** competencies. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Professionalism Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=2}
library(ggplot2)
filter(results, Section == "Professionalism") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., desc(variable), desc(value)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Professionalism") +
  theme(legend.position='top')
```

\newpage

####Program Management

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Program Management** competencies. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Program Management Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=3}
library(ggplot2)
filter(results, Section == "Program Management") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., desc(variable), desc(value)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Program Management") +
  theme(legend.position='top')
```

####Evaluation

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Evaluation** competencies. This distribution shows the competencies with the highest average reported **Desired** skill level near the top and the lowest reported average level near the bottom.

```{r Evaluation Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.height=3.8}
library(ggplot2)
filter(results, Section == "Evaluation") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., desc(variable), desc(value)) -> graph

ggplot(graph, aes(x = reorder(Competency, value, FUN = max), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  ggtitle("Evaluation") +
  theme(legend.position='top')
```

\newpage

###Part C: Skills, Knowledge, and Processes Important to You

For **Part C** of the PfS / DDPI Staff Assessment survey all participants rated how important each of the following skills, knowledge areas, and processes were for their job.

```{r create Part C data, echo=FALSE, warning=FALSE, message=FALSE}
CResults <- data.frame(
  c('Collaboration among co-workers and divisions',
'Developing clear and assertive communications skills',
'Conducting effective and efficient meetings',
'Listening carefully',
'Encouraging teamwork and collaboration',
'Constructively receiving criticism',
'Providing constructive feedback',
'Leading people and delegating tasks to achieve goals',
'Empowering others to achieve results and holding them accountable',
'Motivating others in order to reach program and organizational goals',
'Influencing others in a way that results in consensus and agreement',
'Understanding organization mission and vision',
'Understanding program priorities and goals',
'Understanding the big picture',
'Access to continuous learning and new knowledge acquisition opportunities',
'Access to professional development opportunities',
'Access to a mentor to assist with professional development',
'Establishing and tracking goals and objectives',
'Establishing work plans and timeframes',
'Taking appropriate and timely action to address unexpected changes',
'Communicating regularly with your peer officer group',
'Communicating regularly with cross-peer officer groups',
'Meeting with the PfS/DDPI Program Director to discuss new ideas',
'Meeting with the PfS/DDPI TA Coordinator to discuss technical assistance',
'Meeting with the PfS/DDPI Science Coordinator to discuss ideas',
'Conducting regular meetings with direct reports to discuss performance',
'Communicating program concerns and challenges with supervisors',
'Recognizing and rewarding people for doing their best'),
c('Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Skills',
'Knowledge',
'Knowledge',
'Knowledge',
'Knowledge',
'Knowledge',
'Knowledge',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes',
'Processes'))

PartC <- data.frame(
survey[, 'Q14.2_1'],
survey[, 'Q14.2_2'],
survey[, 'Q14.2_3'],
survey[, 'Q14.2_4'],
survey[, 'Q14.2_5'],
survey[, 'Q14.2_6'],
survey[, 'Q14.2_7'],
survey[, 'Q14.2_8'],
survey[, 'Q14.2_9'],
survey[, 'Q14.2_10'],
survey[, 'Q14.2_11'],
survey[, 'Q14.3_1'],
survey[, 'Q14.3_2'],
survey[, 'Q14.3_3'],
survey[, 'Q14.3_4'],
survey[, 'Q14.3_5'],
survey[, 'Q14.3_6'],
survey[, 'Q14.4_1'],
survey[, 'Q14.4_2'],
survey[, 'Q14.4_3'],
survey[, 'Q14.4_4'],
survey[, 'Q14.4_5'],
survey[, 'Q14.4_6'],
survey[, 'Q14.4_7'],
survey[, 'Q14.4_8'],
survey[, 'Q14.4_9'],
survey[, 'Q14.4_10'],
survey[, 'Q14.4_11'])

colnames(CResults) <- c("Question","Area")

PartC[PartC == 6] <- NA

CResults$Rating <- colMeans(PartC, na.rm = TRUE)

```

####Skills
`r CResults %>% filter(Area == 'Skills') %>% select(., 'Question','Rating') %>% kable(., digits = 2)`

####Knowledge
`r CResults %>% filter(Area == 'Knowledge') %>% select(., 'Question','Rating') %>% kable(., digits = 2)`

####Processes
`r CResults %>% filter(Area == 'Processes') %>% select(., 'Question','Rating') %>% kable(., digits = 2)`