---
title: "PfS / DDPI Staff Assessment"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r read, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(dplyr)
library(reshape2)

survey = read.csv('data.csv', stringsAsFactors = FALSE)
survey <- survey[3:30,]
survey<- data.frame(data.matrix(survey))
```

##Aggregate report for all participants

```{r create results, echo=FALSE, warning=FALSE, message=FALSE}
Current <- data.frame(survey[,'Q4.2_1'],
survey[,'Q4.3_1'],
survey[,'Q4.4_1'],
survey[,'Q4.5_1'],
survey[,'Q4.6_1'],
survey[,'Q4.7_1'],
survey[,'Q4.8_1'],
survey[,'Q4.9_1'],
survey[,'Q4.10_1'],
survey[,'Q4.11_1'],
survey[,'Q4.12_1'],
survey[,'Q4.13_1'],
survey[,'Q4.14_1'],
survey[,'Q4.15_1'],
survey[,'Q4.16_1'],
survey[,'Q6.2_1'],
survey[,'Q6.3_1'],
survey[,'Q6.4_1'],
survey[,'Q6.5_1'],
survey[,'Q6.6_1'],
survey[,'Q7.2_1'],
survey[,'Q7.3_1'],
survey[,'Q7.4_1'],
survey[,'Q7.5_1'],
survey[,'Q7.6_1'],
survey[,'Q7.7_1'],
survey[,'Q7.8_1'],
survey[,'Q8.2_1'],
survey[,'Q8.3_1'],
survey[,'Q8.4_1'],
survey[,'Q8.5_1'],
survey[,'Q9.2_1'],
survey[,'Q9.3_1'],
survey[,'Q10.2_1'],
survey[,'Q10.3_1'],
survey[,'Q10.4_1'],
survey[,'Q10.5_1'],
survey[,'Q10.6_1'],
survey[,'Q11.2_1'],
survey[,'Q11.3_1'],
survey[,'Q12.2_1'],
survey[,'Q12.3_1'],
survey[,'Q12.4_1'],
survey[,'Q12.5_1'],
survey[,'Q12.6_1'],
survey[,'Q12.7_1'],
survey[,'Q13.2_1'],
survey[,'Q13.3_1'],
survey[,'Q13.4_1'],
survey[,'Q13.5_1'],
survey[,'Q13.6_1'],
survey[,'Q13.7_1'],
survey[,'Q13.8_1'],
survey[,'Q13.9_1'])

Desired <- data.frame(survey[,'Q4.2_2'],
survey[,'Q4.3_2'],
survey[,'Q4.4_2'],
survey[,'Q4.5_2'],
survey[,'Q4.6_2'],
survey[,'Q4.7_2'],
survey[,'Q4.8_2'],
survey[,'Q4.9_2'],
survey[,'Q4.10_2'],
survey[,'Q4.11_2'],
survey[,'Q4.12_2'],
survey[,'Q4.13_2'],
survey[,'Q4.14_2'],
survey[,'Q4.15_2'],
survey[,'Q4.16_2'],
survey[,'Q6.2_2'],
survey[,'Q6.3_2'],
survey[,'Q6.4_2'],
survey[,'Q6.5_2'],
survey[,'Q6.6_2'],
survey[,'Q7.2_2'],
survey[,'Q7.3_2'],
survey[,'Q7.4_2'],
survey[,'Q7.5_2'],
survey[,'Q7.6_2'],
survey[,'Q7.7_2'],
survey[,'Q7.8_2'],
survey[,'Q8.2_2'],
survey[,'Q8.3_2'],
survey[,'Q8.4_2'],
survey[,'Q8.5_2'],
survey[,'Q9.2_2'],
survey[,'Q9.3_2'],
survey[,'Q10.2_2'],
survey[,'Q10.3_2'],
survey[,'Q10.4_2'],
survey[,'Q10.5_2'],
survey[,'Q10.6_2'],
survey[,'Q11.2_2'],
survey[,'Q11.3_2'],
survey[,'Q12.2_2'],
survey[,'Q12.3_2'],
survey[,'Q12.4_2'],
survey[,'Q12.5_2'],
survey[,'Q12.6_2'],
survey[,'Q12.7_2'],
survey[,'Q13.2_2'],
survey[,'Q13.3_2'],
survey[,'Q13.4_2'],
survey[,'Q13.5_2'],
survey[,'Q13.6_2'],
survey[,'Q13.7_2'],
survey[,'Q13.8_2'],
survey[,'Q13.9_2'])

Competency = c('PDMP Statutes and Laws',
'PDMP Implementation/Expansion',
'PDMP Data Sharing and Linking',
'PDMP Integration with Pharmacy Software',
'PDMP Interstate Data Sharing',
'Heroin/Fentanyl',
'Insurance Mechanisms',
'CDC Prescribing Guideline',
'Academic Detailing',
'Naloxone',
'PfS Indicators',
'ICD-10-CM Transition',
'Data Dashboards',
'Program Evaluation',
'Legal/Policy Tools',
'Monthly 1:1 Calls with Awardees',
'APRs/TRs',
'Site Visits ',
'Financial Award Management',
'Understanding of Role',
'Monthly 1:1 Calls with Awardees',
'Responsiveness to Scientific TA Requests',
'Using Quantitative Analytic Techniques',
'Using Qualitative Analytic Techniques',
'Annual Progress Reports (APR)/Technical Reviews (TR)',
'Site Visits',
'Understanding  of Role',
'Monthly 1:1 Calls with Awardees',
'APRs/TRs',
'Site Visits',
'Site Visits',
'Support to States',
'Support to SSTs',
'Relationship Building w/ States',
'Relationship Building w/Program Partners',
'Relationship Building w/in State Support Teams (SST)',
'Effective Communication',
'Conflict Management/Resolution',
'Accountability',
'Ongoing Learning and Professional Development',
'Program Development, Improvement and Evaluation',
'Fostering Collaboration and Leveraging Resources',
'Time Management',
'Providing TA to States',
'Decision Making',
'Individual Project Management',
'Program Evaluation',
'Engaging Stakeholders',
'Describing the Program/Project',
'Focusing the Evaluation Design',
'Development of IRB and OMB Packages',
'Gathering Credible Evidence',
'Justifying Conclusions',
'Ensuring Use and Sharing Lessons Learned')

Section = c('Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Topical',
'Project Officer',
'Project Officer',
'Project Officer',
'Project Officer',
'Project Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Science Officer',
'Evaluation Officer',
'Evaluation Officer',
'Evaluation Officer',
'Evaluation Officer',
'Subject Matter Expert',
'Subject Matter Expert',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Interpersonal',
'Professionalism',
'Professionalism',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Program Management',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation',
'Evaluation')

Part = c('A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'A',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B',
'B')

results <- data.frame(Competency,Part,Section)

colnames(Current) <- Competency
colnames(Desired) <- Competency

results$Current <- colMeans(Current, na.rm = TRUE)
results$Desired <- colMeans(Desired, na.rm = TRUE)

```
The PfS / DDPI Staff Assessment survey was divided into three parts, including:

- **Part A: Topical and Role-Specific Competencies**
- **Part B: Functioning Competencies**
- **Part C: Skills, Knowledge, and Processes Important to You**

###Part A: Topical and Role-Specific Competencies

For **Part A** of the PfS / DDPI Staff Assessment survey all participants were asked to rate their **Current** and **Desired** level for each of a set of listed competencies.

- **Current** skill level was defined as your present level of competency in a particular skill or area
- **Desired** level was defined as the level of ability you were interested in attaining for a particular skill or knowledge area in the future

The figure below illustrates the distribution of both **Current** and **Desired** skill levels for all **Topical and Role-Specific Competencies**.

This distribution illustrates areas of strength (competencies near the top) and areas where growth and training may be needed (competencies  near the bottom).

```{r Overall Bar Graph, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%"}
library(ggplot2)
filter(results, Section == "Topical") %>%
select(Competency, Current, Desired) %>%
  melt(.,id.vars="Competency") %>%
  arrange(., Competency, desc(variable)) -> graph

ggplot(graph, aes(x = reorder(Competency, value), y = value, fill=variable)) +
  geom_bar(stat='identity',position='identity',alpha=.9) +
  labs(x = "Topical or Role-Specific Competency", y="Average Level Reported", fill="Rating") +
  scale_fill_manual(labels = c("Current", "Desired"), values = c("grey60", "grey20")) +
  coord_flip(ylim = c(1,6)) +
  geom_hline(yintercept = c(2,4,6), color = 'grey30') +
  scale_y_continuous(breaks = c(2,4,6), labels = c("Awareness","Application","Mastery")) +
  geom_text(aes(label=round(value, digits = 2)), hjust=1, color = "grey90", size=3.25) +
  theme(legend.position='top')
```

